Sketch Recogniton using Particle Swarm Algorithm

### 2009-04-12 draft/System.tex

\subsection{Choosing the best fit}
The two PSO algorithms produce two segmentation solutions. After that the system evaluates each solution to finally select the best segmentation. This evaluation is based on the area of both the segmentation and the input stroke. Equation \ref{eq:bestFit1} and \ref{eq:bestFit2} are used to evaluate each segmentation.

\begin{equation}
\label{eq:bestFit1}
E_{area}=A_{st}-A_{sg}
 \end{equation}
 \begin{equation}
\label{eq:bestFit2}
E_{tot}=E_{area}+E_{alg}
 \end{equation}
 where $A_{st}$ is the area of the input stroke, $A_{sg}$ is area of computed segmenation, $E_{alg}$ is the approximation error of the segmentation. The segmentation which crosspond to the minimum $E_{tot}$ is the best segmentation.

\section{Hybird Segmentation Algorithm}
\label{sec:BenchMarckAlgorithm}

In this research, we developed another algorithm as reference to the results obtained by the DPSO algorithms. The algorithm was first implemented by  Sezgin et al. in \cite{earlyprocess}. The algorithm is divided into the following steps: 
\begin{enumerate}
	\item Compute the curvature and the speed for each point in the stroke. 
	\item   A percentage of maximum value of the speed and curvature is used as threshold.
		\item Mark the values higher than the threshold in a new arrays $L_c$ as the list of corner points generated from the curvature curve. The list $L_s$ contains the points generated from the speed curve.
	\item Compute a confidence on each list based on the type of curve. Then sort the lists $L_s$and $L_c$ by the confidence value. 
	\item Find the intersection points in both list and generate the a Sample solution $h_{curr}$. 
	\item Use $h_{curr}$ as initial solution. Loop doing the following:

@@

\begin{description}
 \item [Structural and geometrical Features(FS1)] Features defines the structure of the geometrical symbol.  
\begin{description}
	 \item[No. Of segments] Number of segments in the symbol. 
		\item[No. Of primitives] Number of primitives in the symbol. The feature helps when identifying             symbols with mixed geometric primitives like cylinders and callouts.  
		\item [No. of curves] Number of curves or ellipses in the symbol. 
		\item [No. of lines] Number of lines in the symbol. 
		\item [No. of perpendicular lines] Number of perpendicular lines. 
		\item [No. of parallel lines] Number of parallel lines. 
		\item [No. of intersections] Number of intersection between lines and curves. 
		\item [Size Ratio] Ratio between width to height of the symbol.
		%\item[No. of holes] Number of holes in the symbols.

>>>>

\subsection{Choosing the best fit}
The two PSO algorithms produce two segmentation solutions. After that the system evaluates each solution to finally select the best segmentation. This evaluation is based on the area of both the segmentation and the input stroke. The segmentation error($E_{alg}$ in Equation \ref{eq:bestFit2})represents the sum of Square Root Error of the length from the point on the stroke to the estimated curve or line. In \textsl{AlgS2}, this error is the same as the computed error in Equation \ref{eq:ErrorSwarm1} but For the second algorithm \textsl{AlgS2} it is different than the computed error in Equation \ref{eq:errorSwarm2}. The additional computation is necessary to  compare the two segmentation fairly. 
\begin{equation}
\label{eq:bestFit1}
E_{area}=A_{st}-A_{sg}
 \end{equation}
 \begin{equation}
\label{eq:bestFit2}
E_{tot}=E_{area}+E_{alg}
 \end{equation}
 where $A_{st}$ is the area of the input stroke, $A_{sg}$ is area of computed segmenation, $E_{alg}$ is the Segmentation Error. The segmentation which crosspond to the minimum $E_{tot}$ is the best segmentation.

\section{Hybird Segmentation Algorithm \textsl{Alg3}}
\label{sec:BenchMarckAlgorithm}

In this research, we developed another algorithm as reference to the results obtained by the DPSO algorithms. The algorithm was first implemented by  Sezgin et al. in \cite{earlyprocess}. The algorithm is divided into the following steps: 
\begin{enumerate}
	\item Compute the curvature and the speed for each point in the stroke. 
	\item   A percentage of maximum value of the speed and curvature is used as threshold.
		\item Mark the values higher than the threshold in a new arrays $L_c$ as the list of corner points generated from the curvature curve. The list $L_s$ contains the points generated from the speed curve.
	\item Compute a confidence on each list based on the type of curve. Then sort the lists $L_s$and $L_c$ by the confidence value. 
	\item Find the intersection points in both list and generate the a Sample solution $h_{curr}$. 
	\item Use $h_{curr}$ as initial solution. Loop on the following:

@@

\begin{description}
 \item [Structural and geometrical Features(FS1)] Features defines the structure of the geometrical symbol.  
\begin{description}
	 \item[Segments] Number of segments in the symbol.
	 \item [Strokes] Number of strokes or partical strokes that created the symbols.  
		\item[Primitives] Number of primitives in the symbol. The feature helps when identifying             symbols with mixed geometric primitives like cylinders and callouts.  
		\item [Curves] Number of curves or ellipses in the symbol. 
		\item [Lines] Number of lines in the symbol. 
		\item [Perpendicular lines] Number of perpendicular lines. 
		\item [Parallel lines] Number of parallel lines. 
		\item [Intersections] Number of intersection between lines and curves. 
		\item [T intersections] Number of T intersections. 
		\item [L intersections] Number of L intersections. 
		\item [X intersections] Number of X intersections.
		\item [Size Ratio] Ratio between width to height of the symbol.

		%\item[No. of holes] Number of holes in the symbols.
